### 2022-07-27 paper/localpsf.tex
small typo when stating the generalized eigenvalue problem in the caption of the plot

\begin{figure}
	\begin{subfigure}{0.59\textwidth}
		\begin{center}
			\begin{tikzpicture}[baseline, trim axis right]
			\begin{axis}[width=0.99\linewidth, height=0.8\linewidth,
			ymode=log,
			xmin=-50,
			xmax=1450,
			ymax=1.e4,
			xlabel={$k$, generalized eigenvalue \#},
			ylabel={$\lambda_{k}$},
			xtick={0, 300, 600, 900, 1200},
			%legend pos=north east,
			legend style={font=\small},
			ylabel near ticks, ylabel shift={-6pt},
			axis x line*=bottom,
			axis y line*=left,
			legend style={at={(0.95,1)},anchor=north east},
			title={Generalized eigenvalues, $\bm{H} \bm{u}_{k}=\lambda_{k} \bm{\preconditioner} \bm{u}_{k}$}
			]
			\addlegendentry{REG}
			\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues.dat};
			\addlegendentry{PSF (1)}
			\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues.dat};
			\addlegendentry{PSF (5)}
			\addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues.dat};
			\addlegendentry{PSF (25)}
			\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues.dat};
			\end{axis}
			\end{tikzpicture}
		\end{center}
		\caption{}
		\label{fig:generalized_eigenvalues}
	\end{subfigure}
	\begin{subfigure}{0.39\textwidth}
		\begin{center}
			\begingroup
			\setlength{\tabcolsep}{4pt}
			\renewcommand{\arraystretch}{1.25}
			\begin{tabular}{c| c c}
				& $\kappa(\bm{\preconditioner}^{-1} \bm{H})$ &	$\kappa(\bm{\preconditioner}^{-1} \bm{H}_{\text{gn}})$ \\
				\hline 
				REG        & \verb~7.02e+3~ & \verb~7.02e+3~ \\
				NONE       & \verb~8.71e+2~ & \verb~9.22e+2~ \\
				PSF $(1)$  & \verb~1.75e+1~ & \verb~1.76e+1~ \\
				PSF $(5)$  & \verb~1.39e+1~ & \verb~1.39e+1~ \\
				PSF $(25)$ & \verb~1.03e+1~ & \verb~1.06e+1~
			\end{tabular}
			\endgroup
		\end{center}
		\caption{}
		\label{fig:condition_number}
	\end{subfigure}
	\caption{Left (\ref{fig:generalized_eigenvalues}): eigenvalues for generalized eigenvalue problem $\bm{H} \bm{u}_k = \lambda_k \bm{\preconditioner}_k$. Here $\bm{H}$ is the Hessian and $\bm{\preconditioner}$ is the PSF approximation constructed using the Gauss-Newton Hessian, $\bm{H}_\text{gn}$, for 1, 5, and 25 batches (PSF (1), PSF (5), and PSF (25), respectively), or the regularization Hessian (REG). Right (\ref{fig:condition_number}): condition number, $\kappa$, for $\bm{\preconditioner}^{-1} \bm{H}$ and $\bm{\preconditioner}^{-1} \bm{H}_\text{gn}$ for these different preconditioners, and no preconditioner (NONE). All operators are evaluated at the $\bm{\basalfriction}$ that solves the inverse problem for $\gamma=7.3 \times 10^3$, as determined by the Morozov discrepancy principle.}
\end{figure}

>>>>

\begin{figure}
	\begin{subfigure}{0.59\textwidth}
		\begin{center}
			\begin{tikzpicture}[baseline, trim axis right]
			\begin{axis}[width=0.99\linewidth, height=0.8\linewidth,
			ymode=log,
			xmin=-50,
			xmax=1450,
			ymax=1.e4,
			xlabel={$k$, generalized eigenvalue \#},
			ylabel={$\lambda_{k}$},
			xtick={0, 300, 600, 900, 1200},
			%legend pos=north east,
			legend style={font=\small},
			ylabel near ticks, ylabel shift={-6pt},
			axis x line*=bottom,
			axis y line*=left,
			legend style={at={(0.95,1)},anchor=north east},
			title={Generalized eigenvalues, $\bm{H} \bm{u}_{k}=\lambda_{k} \bm{\preconditioner} \bm{u}_{k}$}
			]
			\addlegendentry{REG}
			\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues.dat};
			\addlegendentry{PSF (1)}
			\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues.dat};
			\addlegendentry{PSF (5)}
			\addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues.dat};
			\addlegendentry{PSF (25)}
			\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues.dat};
			\end{axis}
			\end{tikzpicture}
		\end{center}
		\caption{}
		\label{fig:generalized_eigenvalues}
	\end{subfigure}
	\begin{subfigure}{0.39\textwidth}
		\begin{center}
			\begingroup
			\setlength{\tabcolsep}{4pt}
			\renewcommand{\arraystretch}{1.25}
			\begin{tabular}{c| c c}
				& $\kappa(\bm{\preconditioner}^{-1} \bm{H})$ &	$\kappa(\bm{\preconditioner}^{-1} \bm{H}_{\text{gn}})$ \\
				\hline 
				REG        & \verb~7.02e+3~ & \verb~7.02e+3~ \\
				NONE       & \verb~8.71e+2~ & \verb~9.22e+2~ \\
				PSF $(1)$  & \verb~1.75e+1~ & \verb~1.76e+1~ \\
				PSF $(5)$  & \verb~1.39e+1~ & \verb~1.39e+1~ \\
				PSF $(25)$ & \verb~1.03e+1~ & \verb~1.06e+1~
			\end{tabular}
			\endgroup
		\end{center}
		\caption{}
		\label{fig:condition_number}
	\end{subfigure}
	\caption{Left (\ref{fig:generalized_eigenvalues}): eigenvalues for generalized eigenvalue problem $\bm{H} \bm{u}_k = \lambda_k \bm{\preconditioner} \bm{u}_k$. Here $\bm{H}$ is the Hessian and $\bm{\preconditioner}$ is the PSF approximation constructed using the Gauss-Newton Hessian, $\bm{H}_\text{gn}$, for 1, 5, and 25 batches (PSF (1), PSF (5), and PSF (25), respectively), or the regularization Hessian (REG). Right (\ref{fig:condition_number}): condition number, $\kappa$, for $\bm{\preconditioner}^{-1} \bm{H}$ and $\bm{\preconditioner}^{-1} \bm{H}_\text{gn}$ for these different preconditioners, and no preconditioner (NONE). All operators are evaluated at the $\bm{\basalfriction}$ that solves the inverse problem for $\gamma=7.3 \times 10^3$, as determined by the Morozov discrepancy principle.}
\end{figure}
